---
title: "Import_offtakes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Import_offtakes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# install.packages("pak")
# pak::pak("inrae/rsic2")
library(rsic2)
```

## SIC project definition

```{r}
cfg <- loadConfig(sic_path = "C:/DocDD/Inrae/SIC/Versions/Sic538i5", 
                  xml_path = file.path(getwd(), "test.xml"), 
                  new_project = TRUE)
```


## Data importation

```{r}
df <- openxlsx2::read_xlsx("Data_ouvrages.xlsx")
df$id <- paste("ouvrage", df$`ID Ouvrage`)
```

Plot map

```{r}
library(leaflet)
library(sf)
sf_nodes <- st_as_sf(df, coords = c("X", "Y"), crs = 2154)
sf_nodes_wgs84 <- st_transform(sf_nodes, crs = 4326)
leaflet(sf_nodes_wgs84) %>%
  addTiles() %>%
  addCircleMarkers(
    lng = ~ st_coordinates(sf_nodes_wgs84)[, 1],
    lat = ~ st_coordinates(sf_nodes_wgs84)[, 2],
    label = ~ df$id,
  )
```


## Create reach objects between nodes

We format the data frame to create the reach objects.

```{r}
df$section_type <- "R"
df$section_type[!is.na(df$DN_mm)] <- "C"
df$section_width <- df$`Largeur_Section (cm)` / 100
df$section_radius <- df$DN_mm / 2000
df$section_bottom_elevation <- df$Z
df$section_height <- df$`Hauteur_Section (m)` / 100
df$abscissa <- 0
for (i in seq(2, nrow(df))) {
  df$abscissa[i] <- df$abscissa[i-1] + sqrt((df$X[i] - df$X[i-1])^2 + (df$Y[i] - df$Y[i-1])^2)
}
df$regulator <- grepl("regulation", df$Type_ouv)
```

We create a function for creating a reach object from a table representing sections objects.

```{r}
create_reach_from_sections <- function(df) {
  lapply(seq(nrow(df)), function(i) {
    if (df$section_type[i] == "R") {
      profile <- list(B = df$section_width[i], 
                      ZF = df$section_bottom_elevation[i], 
                      ZB = df$section_bottom_elevation[i] + df$section_height[i])
    } else if (df$section_type[i] == "C") {
      profile <- list(R = df$section_radius[i], 
                      ZF = df$section_bottom_elevation[i], 
                      ZB = df$section_bottom_elevation[i] + df$section_radius[i] * 2)
    }
    create_section_txt(section_name = df$id[i], 
                       abscissa = df$abscissa[i], 
                       section_type = df$section_type[i], 
                       profile = profile, 
                       singular = df$regulator[i], 
                       xgeo = df$X[i],
                       ygeo = df$Y[i])
  })
}
```

Remove duplicate rows.

```{r}
df <- df[which(!duplicated(df$abscissa)), ]
```


We generate a reach object from the table using the function we created.

```{r}
sections <- create_reach_from_sections(df)
```

And then we split this reach into multiple reaches using location of offtakes.

```{r}
rows_nodes <- which(!df$regulator)
if (df$regulator[nrow(df)]) {
  # The last row is a regulator: we need to add a downstream node
  rows_nodes <- c(rows_nodes, nrow(df))
}
reaches <- lapply(seq_along(rows_nodes)[-1], function(i) {
  sections[seq(rows_nodes[i-1], rows_nodes[i])]
})
```

## Import the reaches into SIC

```{r}
sic_import_reaches(reaches, import_mode = "ImportXml_NEW", cfg = cfg)
```

Set some project parameter:

```{r}
set_project_params(list(DX = 100, 
                        GeoUnit = 2), 
                   cfg = cfg)
```

Add node names for facilitating searches in the network:

```{r}
# Extract rows concerning nodes from the table
df_nodes <- df[rows_nodes, ]
update_nodes_names(new_names = df_nodes$id,
                   cfg = cfg)
```

Update reach connectivity to take branches into account:

```{r}
rows_to_relocate <- which(!is.na(df_nodes$Noeud_amont))
xp <- xml2::read_xml(cfg$project$path)
for (i in rows_to_relocate) {
  num_upstream_node <- get_xml_node_num_by_name(paste("ouvrage", df_nodes$Noeud_amont[i]), xp = xp)
  num_downstream_node <- get_xml_node_num_by_name(paste("ouvrage", df_nodes$`ID Ouvrage`[i]), xp = xp)
  num_reach <- get_xml_reach_num_by_node_num(num_downstream_node, upstream = FALSE, xp = xp)
  node <- xml2::xml_find_first(xp, sprintf("/Reseau/Liste_Biefs/Bief[%i]/Top/NoeudAm", num_reach))
  xml2::xml_text(node) <- as.character(num_upstream_node)
  # Copy a section adjacent to the new upstream node in place of the old one
  section_num <- get_xml_section_num_by_name(paste("ouvrage", df_nodes$Noeud_amont[i]), xp = xp)
  copy_xml_section(source_reach = section_num[1], 
                   source_section = section_num[2],
                   target_reach = num_reach,
                   target_section = 1, 
                   xp = xp, 
                   write_xml = FALSE)
  message("Replaced upstream node of reach num ", num_reach, " with the node ", num_upstream_node)
}
xml2::write_xml(xp, cfg$project$path)
```

We add geolocation on the nodes and compute the coordinates of the nodes in the 
EdiSIC display  and the middle point of the reaches.

```{r}
# Manually enter coordinates of 2 nodes in EdiSic display (pixel coords)
# to match EdiSIC background image with geoloc
display_xy <- data.frame(num = which(df_nodes$id %in% c("ouvrage 4", "ouvrage 44")),
                         x = c(341, 592),
                         y = c(54, 467))
add_node_geoloc(x = df_nodes$X, 
                y = df_nodes$Y, 
                display_xy = display_xy,
                cfg = cfg)

```


Now that some reaches have been moved, we need to update the abscissas of the sections
in each reach:

```{r}
xp <- xml2::read_xml(cfg$project$path)
xml_reaches <- xml2::xml_find_all(xp, "/Reseau/Liste_Biefs/Bief")
lapply(xml_reaches, function(xml_reach) {
  xml_sections <- xml2::xml_find_all(xml_reach, "Liste_Sections/SectionMin")
  abscissa <- 0
  previous_coords <- NULL
  for (i in seq_along(xml_sections)) {
    coords <- get_xml_geoloc(xml_sections[[i]])
    if (i > 1) {
      abscissa <- abscissa + sqrt((coords[1] - previous_coords[1])^2 + (coords[2] - previous_coords[2])^2)
    }
    xml_sections[[i]] |> 
      xml2::xml_set_attr("abscisse", as.character(abscissa))
    previous_coords <- coords
  }
}) |> invisible()
xml2::write_xml(xp, cfg$project$path)
```


## Run Talweg on it

```{r}
cfg$sic$fortran$prms$INTERF <- 2 # visible interface (web license key bugs with INTERF=0)
sic_run_mesh(cfg = cfg)
```

## Import regulators

```{r}
xml_regulator <- xml2::read_xml("template_regulator.xml")
xp <- xml2::read_xml(cfg$project$path)
xPath_regulator <- "//SectionMin[@Nom='%s']"
for (i in which(df$regulator)) {
  node_width <- xml2::xml_find_first(xml_regulator, "//Largeur")
  xml2::xml_text(node_width) <- as.character(df$`Largeur_ouv (cm)`[i] / 100)
  node_bottom_elevation <- xml2::xml_find_first(xml_regulator, "//CoteRadier")
  xml2::xml_text(node_bottom_elevation) <- as.character(df$Z[i])
  node_opening <- xml2::xml_find_first(xml_regulator, "//Ouverture")
  xml2::xml_text(node_opening) <- as.character(df$`Hauteur_ouv (m)`[i] / 100)
  
  node_regulator <- xml2::xml_find_first(xp, sprintf(xPath_regulator, df$id[i]))
  xml2::xml_add_child(node_regulator, xml_regulator)
}
xml2::write_xml(xp, cfg$project$path)
```


## Import offtakes

```{r}
xp <- xml2::read_xml(cfg$project$path)
xPath_node <- "/Reseau/Liste_Noeuds/Noeud[@Nom='%s']"
for (i in seq(nrow(df_nodes))) {
  xml_offtake <- xml2::read_xml("template_offtake.xml")
  if (is.na(df_nodes$`DN (mm)`[i])) {
    # Rectangular gate
    node_circular_gate <- xml2::xml_find_first(xml_offtake, "//Ouvrage[@Type='VanneC']")
    xml2::xml_remove(node_circular_gate)
  } else {
    # Circular gate
    node_rectangular_gate <- xml2::xml_find_first(xml_offtake, "//Ouvrage[@Type='VanneR']")
    xml2::xml_remove(node_rectangular_gate)
  }
  node_width <- xml2::xml_find_first(xml_offtake, "//Largeur")
  if (is.na(df_nodes$`DN (mm)`[i])) {
    # Rectangular gate
    xml2::xml_text(node_width) <- as.character(df_nodes$`Largeur_ouv (cm)`[i] / 100)
  } else {
    # Circular gate
    xml2::xml_text(node_width) <- as.character(df_nodes$`DN (mm)`[i] / 1000)
  }
  
  node_bottom_elevation <- xml2::xml_find_first(xml_offtake, "//CoteRadier")
  xml2::xml_text(node_bottom_elevation) <- as.character(df_nodes$Z[i])
  node_opening <- xml2::xml_find_first(xml_offtake, "//Ouverture")
  xml2::xml_text(node_opening) <- as.character(df_nodes$`Hauteur_ouv (m)`[i] / 100)
  node_down_elevation <- xml2::xml_find_first(xml_offtake, "//CoteFixe")
  xml2::xml_text(node_down_elevation) <- as.character(df_nodes$Z[i])
  
  node_offtake <- xml2::xml_find_first(xp, sprintf(xPath_node, df_nodes$id[i]))
  xml2::xml_add_child(node_offtake, xml_offtake)
}
xml2::write_xml(xp, cfg$project$path)
```


